\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{parskip}
\usepackage{enumerate}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{fullpage}
\usepackage[colorlinks]{hyperref}

\newtheorem{defn}{Definition}[section]

\numberwithin{equation}{section}
\begin{document}

\title{CS 341 Notes}
\author{Matthew Visser}
\date{Nov  3, 2011}
\maketitle

\section{Graph Searching}

\begin{defn}
	A \textbf{bridge} is an edge that exists in all possible spanning trees.
	If a bridge is removed, it will disconnect the graph.
\end{defn}

\begin{defn}
	A \textbf{cut vertex} is a vertex that, when removed, causes the graph to be
	disconnected.  They are also known as \textbf{articulation points}.
	\label{cut-vertex}
\end{defn}

\subsection{DFS}

A directed graph is a lot different.  Our spanning tree may not be connected
even though there is a possible spanning tree that is connected.

\begin{defn}
	A \textbf{cross edge} is an edge that connects two connected parts of a
	directed graph.
\end{defn}

\section{Articulations}

See Definition \ref{cut-vertex}.

\subsection{Motivation}
\begin{itemize}
	\item important in communication networks.
	\item In traffic flow they identify places that will stop traffic between
		two areas of a city if blocked.
\end{itemize}

\subsection{Finding Cut Vertices}

The general idea is to find a node with which no descendant has a back edge to
the node's parent.

We need to computer \texttt{low[v]}.
\begin{itemize}
	\item Need another function defined on vertices
	\item This quantity will be used in our articulation algorithm.
\end{itemize}

\begin{equation}
	\texttt{low}[v] = \min\{d[v],d[z] \text{ s.t. }  (u,z) \text{ is a back edge
	for some descendant $u$ of $v$.}
	\label{eq:low}
\end{equation}

See an example of how to calculate this in the slides along with the algorithm.

\subsection{Minimum Spanning Trees}

With a weighted graph, we want a tree that has the smallest sum of edge values.

Motivation: connecting machines with a minimum amount of wire, \textit{etc}.


\end{document}
% vim: tw=80
